---
title: "Analysis on used cars"
date: 2020-10-25
author: "Zsombor Hegedus"
output: pdf_document
        #html_document
  
---



## Introduction

The purpose of this document is to summarise the work done to complete two homeworks.
* The first one is Data exercise 2 in Chapter 1 (p28)
* The second one is Data exercise 2 in Chapter 2 (p55)
 
The task at hand was to collect data on used cars of a specific model form the Web using web scraping and then describe:

* The process of web scraping
* How many observations I collected
* Encountered difficulties
* Cleaning the data 
* Describing the cleaned dataset

All codes and files used for this analysis are avaialbe in this [github repo](https://github.com/zsomborh/ba_da1/tree/master/homework).

## Web-scraping

The website of my choice was hasznaltauto.hu, as this is one of the biggest Hungarian sites advertising used cars. On the opening page of the site, there is a search prompt that asks you what type of car you are looking for. There is a lot of options to choose from in the dropdown where a small number in brackets indicates how many of such vehicles are advertised currently. I briefly looked through all brands and decided to go with a car that has a relatively high number of adverts. This is the Renault Megane.

After choosing the car, I was directed to a site with 20 adverts/page - I will call this a subpage. My first task for the scraping was figuring out a way to scrape every subpage that is related to the Megane advertisements. I needed to go through 58 of such webpages. The way how these distinct pages are represented in URL is by a string in the end with *page* where X denotes the order of a given subpage. To go through each one of them, I generated all 58 URLs with their respective *page* appendage and put them in a list.

After the list of URL links was created, I took one of the subpages and wrote a scraper in Python. The html code behind these subpages was relatively clear and simple and there were a lot of features that I could collect. The Python package, called BeautifulSoup was used for the parsing, and the most common functions that I took were the *.find()* and *.findAll()* functions. The result of the scraping was a Pandas dataframe that I downloaded as a csv file and uploaded to github.

## Challenges faced and data cleaning

The challenges that I needed to face can be grouped into the following categories: 

* Dispersed nature of data: only 20 observations were available for each subpage.
* Hidden layers: price appeared twice due to hidden layers in the html code which I realized at a later stage only making my price list twice as big as the other lists.
* Unnecessary characters: some characters like spaces, or units of measurement were scraped along with the necessary information.
* Missing data: Some ads had missing data that I needed to replace in my dataframe with NAs.

Variables and README file is available in the [github repo](https://github.com/zsomborh/ba_da1/tree/master/homework).

When I started data analysis, there were a few issues that I needed to address and clean my data before I could proceed. First of all Prices variable contained characters such as 'Ft' which stands for Forint. This could be solved easily by replacing the non-number characters using the *gsub* function. However some observations had taxation related information that I needed to filter out with more sophisticated means. At the end of such observations, there was always a string followed by an integer, which marked the final price that someone has to pay for the car, taxes included. I used the separate function and used that specific string **fizetendo** as my separator.

I did further smaller cleaning steps as well namely:

* Dropping observations where price were not available 
* Changing numeric variables to be recognised as numeric with as.numeric function
* I converted Engine variable to factor variable, so that I can use it for further analysis

## Describing the data
 
Table 1 shows a summary of the kez features of used car prices. We have 1147 observations (we deleted 3 where price was NA). Our median is much lower compared to the mean, and the price distribution has a positive skewness with a thick right tail as you can see from Figure 1. Giving a quick overview on prices, the earlier the car was made, the higher it's price will be. 
 
```{r , include = FALSE}


library(tidyverse)
library(moments)
library(scales)
library(ggcorrplot)
library(xtable)

df <- read_csv('../used_cars.csv')

#some values have Fizetendo in their name, we need the price that is after that only. 
df <- df %>% 
    filter(!is.na(Prices)) %>% 
    separate(Prices , 'Fizetend', into = c("first","second")) %>% 
    mutate(Prices = ifelse(!is.na(second), second,first),
           Prices = as.numeric(gsub('[^0-9\\.]','',Prices)),
           first=NULL,
           second=NULL)

df <- df %>% 
    mutate(
        Displacement = as.numeric(Displacement),
        Power_kW = as.numeric(Power_kW),
        Horsepower = as.numeric(Horsepower),
        Km = as.numeric(Km),
        PictureCount = as.numeric(PictureCount),
        Engine = factor(Engine))

df <- df %>% 
    filter(!is.na(Prices))

car_sum <- df %>% 
    summarise(
        mean     = mean(Prices),
        median   = median(Prices),
        std      = sd(Prices),
        iq_range = IQR(Prices), 
        min      = min(Prices),
        max      = max(Prices),
        skew     = skewness(Prices),
        numObs   = sum( !is.na( Prices ) ) )

xtb <- xtable(car_sum,type = "latex", caption = "Summary statistics used Renault Megane cars")

```
```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE }
print(xtb, comment=FALSE, include.rownames=FALSE)
```
```{r , fig.width=8,fig.height=4, fig.cap='Price distribution uf used cars', echo = FALSE  }
#, results = "asis", warning = FALSE, message = FALSE
ggplot( df , aes( x = Prices ) ) +
    geom_histogram( aes(y = ..density..) , alpha = 1, binwidth = 500000, color = 'black', fill = 'white') +
    geom_density( aes(y = ..density..) , alpha = .2 , bw = 500000, color = 'black', fill="#FF6666") +
    scale_x_continuous(labels = comma)+ 
    scale_y_continuous(labels = comma)+ 
    labs(x='Price', y= 'Density')
```

It is worth taking a look at Table 2 and Figure 2 as well. We can see that most of our cars are either run on Patrol or Gasoline, and looks like Petrol run cars on average cost more.  

```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE }

car_sum <- df %>% 
    group_by(Engine) %>% 
    summarise(
        mean     = mean(Prices),
        median   = median(Prices),
        std      = sd(Prices),
        iq_range = IQR(Prices), 
        min      = min(Prices),
        max      = max(Prices),
        skew     = skewness(Prices),
        numObs   = sum( !is.na( Prices ) ) )
```

```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE }

xtb <- xtable(car_sum,type = "latex", caption = "Summary statistics used Renault Megane cars")
print(xtb, comment=FALSE, include.rownames=FALSE)
```


```{r , fig.width=8,fig.height=4, fig.cap='Price distribution of used cars with Gasoline or Petrol engine', echo = FALSE , results = "asis", warning = FALSE, message = FALSE }

engine_df <- df %>% filter(Engine == 'Benzin'| Engine == 'Dízel')

ggplot( engine_df , aes( x = Prices, colour = Engine, fill = Engine ) ) +
    geom_histogram( aes(x = Prices) , alpha = 0.5, binwidth = 500000) +
    scale_x_continuous(labels = comma)+ 
    scale_y_continuous(labels = comma)+ 
    facet_wrap(~Engine)+
    labs(x='Price', y= 'Count')

```

\newpage
Let's uncover further interesting factors - the correlation matrix based on our numeric variables. Since correlation was 1 for HorsePower and Power_Km (they are basically the same, only they are expressed in a different unit of measurement), I dropped the Power_Km variable.

There are three points we can make by looking at Figure 3, all of which are quite intuitive: 

* There is stronger positive correlation between price vs horsepower - people like to speed up fast 
* There is no correlation whatsoever between displacement vs prices - looks like people don't price in the cylinder volume
* Strog negative correlation between km vs prices - People percieve cars that already run a lot to be less reliable perhaps

```{r , include = FALSE}
df$Power_kW <- NULL

corr <- df %>%
    select(Displacement,Horsepower,Km,PictureCount,Prices)
```
```{r , fig.width=8,fig.height=4, fig.cap='Correlation matrix of scraped numeric variables', echo = FALSE , results = "asis", warning = FALSE, message = FALSE }
corr <- cor(corr, use = "pairwise.complete.obs")
ggcorrplot(corr, method = "square",lab = TRUE)
```