---
title: "da_project_Q3"
author: "Fasih Atif"
date: "10/24/2020"
output: html_document
---

### Install required libraries
```{r, message = FALSE, warning=FALSE}
library(tidyverse)
library(ggcorrplot)
library(stringr)
```

### Import data into dataframe "pizza_data"
```{r, message = FALSE, warning=FALSE}
pizza_data <- read_csv("assignment1_v2_2020-10-24_11_59.csv")
```

### Removed km from string and converted to numeric
```{r}
pizza_data <- mutate(pizza_data,"distance_city_center" = as.numeric(gsub("[^0-9\\.]","" , pizza_data$distance_city_center)))
```

# Correlation Matrix
### Selecting relevant columns from main "pizza_data" and calculating correlation
```{r}
select_col <- pizza_data %>%
  filter(city == "Budapest") %>%
  select(user_rating,no_ratings,distance_city_center,margherita_pizza_price,beverage_price)

cor <- cor(select_col, use = "pairwise.complete.obs")
```

### Visualizing the correlation matrix
```{r}
ggcorrplot(cor, method = "square",  type = "lower",lab = TRUE)

```

# Scatter Plots
### Scatter plot for Budapest - user_rating vs price
```{r}
pizza_data %>% filter(city == "Budapest") %>% 
  ggplot(aes(x = user_rating, y = margherita_pizza_price)) + 
  geom_point() + theme_bw() +
  geom_smooth(method = "lm")
```

### Scatter plot for countryside cities - user_rating vs price
```{r}
pizza_data %>% filter(city != "Budapest") %>% 
  ggplot(aes(x = user_rating, y = margherita_pizza_price)) + 
  geom_point() + theme_bw() +
  geom_smooth(method = "lm")

```

### Scatter plot for Budapest - user_rating vs no_ratings
```{r}
pizza_data %>% filter(city == "Budapest") %>% 
  ggplot(aes(x = no_ratings, y = user_rating )) + 
  geom_point() + theme_bw() +
  geom_smooth(method = "lm")

```

### Scatter plot for countryside cities - user_rating vs no_ratings
```{r}
pizza_data %>% filter(city != "Budapest") %>% 
  ggplot(aes(x = no_ratings, y = user_rating )) + 
  geom_point() + theme_bw() +
  geom_smooth(method = "lm")
```


```{r}
pizza_data %>% filter(city == 'Budapest') %>%
  ggplot(aes( x = user_rating, y = no_ratings )) +
  stat_summary_bin( fun = 'mean',
                    geom = 'point', 
                    color = 'red') + theme_bw()
```

